### 2010-06-10 subarchitectures/visualization.sa/trunk/doc/v11n.tex
v11n: docs updated
v11n: docs

\begin{itemize}
   \item Add visualization.sa to SVN externals:
   \begin{Verbatim}[fontsize=\scriptsize,gobble=6]
      $ svn pe svn:externals .
   \end{Verbatim}
   Add the line:
   \begin{Verbatim}[fontsize=\scriptsize,gobble=6]
      ^/code/subarchitectures/visualization.sa/trunk subarchitectures/visualization.sa
   \end{Verbatim}

   % TODO: the script may be in another location
   \item install the required libraries; there is a script in visualization.sa/config
   that you can run:
   \begin{Verbatim}[fontsize=\scriptsize,gobble=6]
      sudo ubuntu-install-deps.sh
   \end{Verbatim}

   \item enable BUILD\_VISUALIZATION\_SA in cmake
\end{itemize}

@@

The first parameter is the name of the {\em view} that will display the UI
element when it is active, not the name of object. This means that the UI
element will be displayed only when an object is displayed in its default view.
When an object is displayed in another view, the UI element won't be available.
\todo{TODO: user-defined views will be able to specify which elements to show}

@@

@@

The display client can send various types of images to the server: raw images, 
\code{Video::Image}, OpenCV's \code{IplImage} and encoded images that are
supported by Qt. An \code{IplImage} can only be sent if OpenCV was enabled
during compilation.
The clients interface for sending images is:

@@

Raw images can have 1 or 3 channels and the specified image size must match the
size of \code{data}. The supported formats of the compressed image are: bmp,
gif, jpeg, jpg, png, pbm, pgm, ppm, tiff, xbm, xpm. It the format is not
specified, Qt will try to deduce the type from \code{data}. An \code{IplImage}
is first converted to a contiguous array of bytes and sent to the server as a
raw image.

@@

>>>>

To get the visualization from the svn, edit the SVN externals in the root
of your CogX system directory:

\begin{Verbatim}[fontsize=\scriptsize,gobble=3]
   $ svn pe svn:externals .
\end{Verbatim}

Add the following line, save and do an svn update:

\begin{Verbatim}[fontsize=\scriptsize,gobble=3]
   ^/code/subarchitectures/visualization.sa/trunk subarchitectures/visualization.sa
\end{Verbatim}

The subarchitecture depends on some external libraries. If they are not
installed, the system may still compile, but some of the features won't be
available. The dependencies can be installed with the script in
visualization.sa/bin:

\begin{Verbatim}[fontsize=\scriptsize,gobble=3]
   sudo visualization.sa/bin/ubuntu-install-deps.sh
\end{Verbatim}

The new subarchitecture must be added to the main file CMakeLists.txt of the 
project. It should be added before any subarchitectures that use visualization
so that the dependent libraries will build correctly. Add the following
block before the first subarchitecture in CMakeLists.txt:

\begin{Verbatim}[fontsize=\scriptsize,gobble=3]
   option(BUILD_SA_VISUALIZATION "Build visualization libraries (Requires QT4)" NO)
   if(BUILD_SA_VISUALIZATION)
      set(VISUALIZATION_INCLUDE_DIRS
         ${COGX_ROOT}/subarchitectures/visualization.sa/src/c++/autogen
         ${COGX_ROOT}/subarchitectures/visualization.sa/src/c++/core
         )
      set(VISUALIZATION_LIBRARIES
         DisplayClient VisualizationData
         )
      add_subdirectory(subarchitectures/visualization.sa)
      add_definitions(-DFEAT_VISUALIZATION)
   endif(BUILD_SA_VISUALIZATION)
\end{Verbatim}

Finally run \code{ccmake} and set \code{BUILD\_VISUALIZATION\_SA} to \code{ON}
to enable the visualization subarchitecture.

@@

The first parameter is the name of the {\em view} that will display the UI
element when it is active, not the name of object. This means that the UI
element will be displayed only when an object is displayed in its default view.
When an object is displayed in another view, the UI element won't be available.
\todo{TODO: user-defined views will be able to specify which UI elements to show}

@@

The objects can be geometrically transformed on the server when they are
displayed. A client side interface is provided to set display transformations
of objects and their parts.

@@

The display client can send various types of images to the server: raw images, 
\code{Video::Image}, OpenCV's \code{IplImage} and encoded images that are
supported by Qt. An \code{IplImage} can only be sent if OpenCV was enabled
during compilation.
The client-side interface for sending images is:

@@

Raw images can have 1 or 3 channels and the specified image size must match the
size of \code{data}. The supported formats of the compressed image are: bmp,
gif, jpeg, jpg, png, pbm, pgm, ppm, tiff, xbm, xpm. If the format is not
specified, Qt will try to deduce the type from \code{data}. An \code{IplImage}
is first converted to a contiguous array of bytes and sent to the server as a
raw image.

@@

Images can only be displayed in 2D contexts. Image objects can be transformed
by defining a $3 \times 3$ transformation matrix that is applied before
the image is drawn.

\subsection{SVG objects}

SVG objects are sent to the server as XML documents which are then interpreted
by the Qt SVG subsystem. Every SVG object can have multiple parts where each
part is defined in a separate XML document.
\todo{TODO: the interface to define the order of drawing for objects and parts
is missing}
The client-side interface for defining SVG objects is:

\begin{Verbatim}[fontsize=\scriptsize,gobble=3]
   void setObject(const std::string& id, const std::string& partId,
         const std::string& xmlData); 
\end{Verbatim}

The function is named \code{setObject} because initially it was planned that
the server will support multiple types of objects. Currently the server
supports only SVG and doesn't check if the SVG file is valid.

SVG objects can only be displayed in 2D contexts. Every part of an object can
be transformed by defining a $3 \times 3$ transformation matrix that is applied
before the part is drawn.
